*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-04 Code/Manuscript_O2.Rmd
knit

Our changing climate is rapidly altering conditions for these specialized clades of marine picophytoplankton. Predictions indicate a net global increase of *P. marinus* cell abundances of 29% [@flombaumPresentFutureGlobal2013{}, along with  poleward latitudinal shifts of at least 10° in marine phytoplankton niches by the end of this century  [@bartonAnthropogenicClimateChange2016] in response to warming waters, with increases in *P. marinus* of approximately 50% in the more poleward regions of their distributions.

>>>>

Our changing climate is rapidly altering conditions for these specialized clades of marine picophytoplankton. Predictions indicate a net global increase of *P. marinus* cell abundances of 29% [@flombaumPresentFutureGlobal2013], along with  poleward latitudinal shifts of at least 10° in marine phytoplankton niches by the end of this century  [@bartonAnthropogenicClimateChange2016] in response to warming waters, with increases in *P. marinus* of approximately 50% in the more poleward regions of their distributions.
